---
title: "Two-level isotropic sequential GP modelling (with FF) -- flow"
output: html_notebook
---


```{r}
library(data.table)
library(mvtnorm)
library(reshape2)
library(ggplot2)
library(crayon)
library(scoringRules)
library(analogue)
```

```{r}
current_directory = getwd()
descriptor_filename = "/df_intra_sb.txt"
energy_filename = "/oxalic_acid_ff_minima_energies.txt"
save_image_directory = getwd()

alpha_structure_id = "1003019125"
beta_structure_id = "10030141758"
```

```{r}
energies = read.table(paste(current_directory, energy_filename, sep = ""),
                      header = TRUE, colClasses = c("character", "numeric", "numeric", "numeric"),  
                      col.names = c("structure_id", "ff_energy", "vasp_energy", "crystal_energy"))
dt_energy = data.table(energies[!is.na(energies$crystal_energy),])
structure_names = sort(unique(as.character(dt_energy$structure_id)))  ## ensuring the same order

dt_energy$low = dt_energy$vasp_energy 
dt_energy$high = dt_energy$crystal_energy 
dt_energy$structure_id = as.character(dt_energy$structure_id)
# sorting by structure name
dt_energy = dt_energy[order(as.character(structure_id))]

df_symmetry = data.table(read.table(paste(current_directory, descriptor_filename, sep = "")))
df_symmetry$structure_id = as.character(df_symmetry$structure_id)
df_symmetry = df_symmetry[structure_id %in% structure_names]
df_symmetry = df_symmetry[order(as.character(structure_id))]            ## sorting by str_lables

n_structures = length(structure_names)   
n_atoms = max(df_symmetry$atom_id)

head(df_symmetry) 
head(dt_energy)
```

```{r}
## Converting symmetry functions into a wide data table 

col_descriptors = 4:ncol(df_symmetry)
n_descriptors = n_atoms * length(col_descriptors)
new_colnames = unlist(lapply(colnames(df_symmetry)[-(1:3)], paste, as.character(df_symmetry$atom_id[1:n_atoms]), sep = "_"))
dt_structures = data.table(dt_energy) 

C = matrix(nrow = 0, ncol = length(new_colnames))
for (s in 1:n_structures) {   ## matrix-to-vector conversion goes by columns
  C = rbind(C, as.vector(as.matrix(df_symmetry[(df_symmetry$structure_id == structure_names[s]), col_descriptors, with = FALSE])))
}
Dist_scaled = as.matrix(dist(C))
dt_structures = cbind(dt_structures, C)
colnames(dt_structures) = c(colnames(dt_structures)[1:6], new_colnames)
dt_structures[1:20, 1:50]
```

Two "loops": the first one generates nested training sets for the PBE response, the second one -- nested training sets for the PBE0.

```{r}
source('maximin_upd.R')
source('Linear_IsoGP_functions.R')
source('plotting_parameters.R')
setwd(current_directory)

### Looping through nested test sets
training_proportion_low = seq(from = 10, to = 70, by = 5)
n_training_iter_low = length(training_proportion_low)
list_training_sets_low = vector("list", n_training_iter_low)

training_proportion_high = seq(from = 10, to = 70, by = 5)
n_training_iter_high = length(training_proportion_high)
list_training_sets_high = vector("list", n_training_iter_high)

training_set = training_set_maximin

```

Determining the training and test sets -- these have been calculated, and are in the "training_sets" folder
```{r}
# for (i in 1:n_training_iter_low) {
#   
#   n_training_low = floor(training_proportion_low[n_training_iter_low-i+1]*n_structures/100)
#   n_test_low = n_structures - n_training_low
#   ## Choose the training set
#   if (i == 1) {
#     alpha_beta_idx = which(structure_names %in% c(alpha_structure_id, beta_structure_id))
#     other_names = structure_names[-alpha_beta_idx]
#     training_idx_low_ = training_set(n_training_low, C_scaled = as.matrix(dt_structures[-alpha_beta_idx, new_colnames, with = FALSE]))
#     training_idx_low = which(structure_names %in% other_names[training_idx_low_])
#     
#     write.table(data.table("pure_PBE0_test_idx" = test_set(training_idx_low)),                 # test set that hasn't been used for training at all
#                 file = glue::glue("{getwd()}/training_sets/pure_test_idx_{max(training_proportion_low)}.txt"))  
#   } else {
#     training_idx_ = training_set(n_training_low, C_scaled = as.matrix(dt_structures[-test_idx_low, new_colnames, with = FALSE])) # choosing from the subset
#     training_idx_low = which(structure_names %in% training_names_low[training_idx_]) # matching back to the original indeces
#   }
#   test_idx_low = test_set(training_idx_low)
#   training_names_low = structure_names[training_idx_low]  # available structures for next round
#   list_training_sets_low[[i]] = training_idx_low
#   
#   # Record the lower training indeces 
#   write.table(data.table("training_idx_low" = training_idx_low), 
#             file = glue::glue("{getwd()}/training_sets/tr_idx_low_{training_proportion_low[n_training_iter_low-i+1]}.txt"))
# 
#   ############################################################      
#   for (j in 1:n_training_iter_high) {
#     
#     n_training_high = floor(training_proportion_high[n_training_iter_high-j+1]*n_training_low/100) 
#     n_test_high = n_structures - n_training_high
#     ## Choose the training set
#     if (j == 1) {
#       training_idx_high_ = training_set_maximin(n_training_high, C_scaled = C[training_idx_low,])    # choosing from the subset
#       training_idx_high = which(structure_names %in% training_names_low[training_idx_high_])    # matching back to the original indeces
#       
#       write.table(data.table("PBE0_test_idx" = test_set(training_idx_high)),                    # the "common" PBE0 test set for this training_set_low
#                 file = glue::glue("{getwd()}/training_sets/PBE0_common_test_{training_proportion_low[n_training_iter_low-i+1]}.txt"))  
#     } else {
#       training_idx_high_ = training_set(n_training_high, C_scaled = as.matrix(dt_structures[-test_idx_high, new_colnames, with = FALSE])) # choosing from the subset
#       training_idx_high = which(structure_names %in% training_names_high[training_idx_high_]) # matching back to the original indeces
#     }
#     test_idx_high = test_set(training_idx_high)
#     training_names_high = structure_names[training_idx_high]  # available structures for next round
#     list_training_sets_high[[j]] = training_idx_high
#     
#     # Record the high training indeces 
#     write.table(data.table("training_idx_high" = training_idx_high), 
#             file = glue::glue("{getwd()}/training_sets/tr_idx_high_{training_proportion_low[n_training_iter_low-i+1]}_
#                               {training_proportion_high[n_training_iter_high-j+1]}.txt"))
#   }
#   #######################################################    
#   
# }
```

The following loops contain the modelling and producing predicitons and plots


I. Fitting the isotropic GP with FF mean for the Lower level accuracy response (Bayesian)
```{r}
## Setting (more or less informative) common prior hyperparameters
# Prior on the between-stricture variance: sigma2 ~ IG(shape=alpha, scale=gamma)
alpha = 1.0
gamma = 1.0
# Prior on the intercept and linear term: mu ~ N(beta_0, sigma2*R)
beta_0 = c(0.0, 0.5) 
R = diag(1.0, 2)
# phi ~ IG (shape=a, scale=b)
a = 2.0
b = 1.0
## Tau2 = 10^(-5)
tau2 = 10^(-5)

## Specifying the distance matrix
D_all= as.matrix(dist(dt_structures[, new_colnames, with = FALSE]))  
```


```{r}
# Tracking errors
mae_low_track = rmse_low_track = rep(0, n_training_iter_low)

# list of PBE predictions and SDs for all points (to be used in PBE0 modelling)
pred_all_PBE = vector("list", n_training_iter_low)   
pred_all_PBE_sd = vector("list", n_training_iter_low)  

# data frames to keep track of predictions, rank predictions, etc.
df_pred_PBE = vector("list", n_training_iter_low)

df_pred_PBE0_pure = vector("list", n_training_iter_low * n_training_iter_high)  # predictions on pure test set
df_pred_PBE0 = vector("list", n_training_iter_low * n_training_iter_high)       # predictions on common test sets within low levels

# correlation between ranks
PBE0_ff_true_rank_corr = PBE0_pred_true_rank_corr = rep(0, n_training_iter_low * n_training_iter_high)
PBE_ff_true_rank_corr = PBE_pred_true_rank_corr= rep(0, n_training_iter_low)

# data frames to keep track of errors
df_error_pure = data.table(expand.grid(training_proportion_low[n_training_iter_low :1], training_proportion_high[n_training_iter_high :1]))
names(df_error_pure) = c("high", "low")   # MAE and RMSE track on pure test set
df_error_pure$seq_mae = df_error_pure$seq_rmse = 0.0
df_error = df_error_pure                  # MAE and RMSE track on "common" test sets within low levels

# plotting uncertainty -- coefficient
sd_coef = 2
```

```{r}
pure_test_idx = sort(read.table(glue::glue("{getwd()}/training_sets/pure_test_idx_{max(training_proportion_low)}.txt"))$pure_PBE0_test_idx)

for (low_iter in 1:n_training_iter_low) {
  
  ## Specifying the response
  dt_energy$energy = dt_energy$low
  ## Reading training and test indices
  training_percentage = training_proportion_low[n_training_iter_low - low_iter + 1] 
  training_idx = sort(read.table(glue::glue("{getwd()}/training_sets/tr_idx_low_{training_percentage}.txt"))$training_idx_low)
  test_idx = sort(read.table(glue::glue("{getwd()}/training_sets/pure_test_idx_{max(training_proportion_low)}.txt"))$pure_PBE0_test_idx)
  n_training = length(training_idx)
  n_test = length(test_idx)

  # Specifying linear part for PBE modelling (ie FF) - training and test
  linear_training = dt_energy[training_idx, ff_energy]
  linear_test = dt_energy[test_idx, ff_energy]
  
  # Optimising the posterior for phi
  phi_opt = phi_iso_optim()
  phi_post = phi_opt$phi_post   
  
  ## Prediction
  y_pred_mean = mu_y(phi_post)
  y_pred_sd = sqrt(diag(Sigma_y(phi_post))*as.numeric(gamma_(phi_post))/alpha_(n_training))
  y_true = as.numeric(dt_energy[test_idx, energy])

  ## Tracking MAE and RMSE
  mae_low_track[low_iter] = mean(abs(dt_energy[test_idx, energy] - y_pred_mean))
  rmse_low_track[low_iter] = get_pred_rmse(y_true, y_pred_mean)

  ## Tracking predicitons and errors
  df_pred_PBE[[low_iter]] = data.frame("structure_id" = dt_structures[test_idx, structure_id],
                      "y_true" = as.numeric(dt_energy[test_idx, energy]),
                      "y_pred" = y_pred_mean,
                      "y_sd" = y_pred_sd,
                      "y_pred_min" = y_pred_mean - sd_coef*y_pred_sd,
                      "y_pred_max" = y_pred_mean + sd_coef*y_pred_sd,
                      "min_dist" = apply(D_all[test_idx, training_idx], 1, min))
  
  ## Looking at ranks: true, predicted and ff
  df_pred_PBE[[low_iter]]$true_rank = rank(df_pred_PBE[[low_iter]]$y_true)
  df_pred_PBE[[low_iter]]$pred_rank = rank(df_pred_PBE[[low_iter]]$y_pred)
  df_pred_PBE[[low_iter]]$ff_rank = rank(dt_energy$ff_energy[pure_test_idx])
 
  # Geting predictions for PBE for all structures
  test_idx = 1:n_structures; n_test = n_structures
  linear_test = dt_energy[test_idx, ff_energy]
  
  pred_all_PBE[[low_iter]] = mu_y(phi_post)     # the function uses test_idx and n_test
  pred_all_PBE_sd[[low_iter]] = sqrt(diag(Sigma_y(phi_post))*as.numeric(gamma_(phi_post))/alpha_(n_training))
  
  # !! Renaming the indeces at lower level -- before modelling the higher level
  training_idx_low = training_idx
  n_training_low = length(training_idx_low) #n_training
  training_names_low = structure_names[training_idx_low]

  ## II. Modelling PBE0 with the trend parameters including PBE
  
  for (high_iter in 1:n_training_iter_high) {
    
    ## Specifying the response
    dt_energy$energy = dt_energy$high
    
    ## Reading training and test indices
    training_proportion = training_proportion_high[n_training_iter_high - high_iter + 1] 
    training_idx = sort(read.table(glue::glue("{getwd()}/training_sets/tr_idx_high_{training_proportion_low[n_training_iter_low-low_iter+1]}_
                                              {training_proportion_high[n_training_iter_high-high_iter+1]}.txt"))$training_idx_high)
    n_training = length(training_idx)
    
    # Test idx -- the common one for the current training low set
    test_idx = sort(read.table(glue::glue("{getwd()}/training_sets/PBE0_common_test_{training_proportion_low[n_training_iter_low-low_iter+1]}.txt"))$PBE0_test_idx)
    n_test = length(test_idx)

    # Specifying linear part - training and test
    linear_training = pred_all_PBE[[low_iter]][training_idx]
    linear_test = pred_all_PBE[[low_iter]][test_idx]                

    # Optimising the posterior for phi_d
    phi_opt = phi_iso_optim()
    phi_post = phi_opt$phi_post

    current_iteration = n_training_iter_high*(low_iter-1) + high_iter

    ## Prediction. MAE
    y_pred_mean = mu_y(phi_post)
    y_pred_var = y_pred_var_high(phi_post, low_variance = (pred_all_PBE_sd[[low_iter]][test_idx])^2)
    y_pred_sd = y_pred_sd_high(y_pred_var)
    y_true = as.numeric(dt_energy[test_idx, energy])

    df_pred_PBE0[[current_iteration]] = data.frame("structure_id" = dt_structures[test_idx, structure_id],
                      "y_true" = as.numeric(dt_energy[test_idx, energy]),
                      "y_pred" = y_pred_mean,
                      "y_sd" = y_pred_sd,
                      "y_pred_min" = y_pred_mean - sd_coef*y_pred_sd,
                      "y_pred_max" = y_pred_mean + sd_coef*y_pred_sd,
                      "min_dist" = apply(D_all[test_idx, training_idx], 1, min))

    df_error$seq_mae[current_iteration] = mean(abs(dt_energy[test_idx, energy] - y_pred_mean))
    df_error$seq_rmse[current_iteration] = get_pred_rmse(y_true, y_pred_mean)
    
    ##########################################
    ###### Looking at PBE0 predictions at pure_test_set only
    ##########################################
    
    test_idx = sort(pure_test_idx)
    n_test = length(test_idx)
    linear_test = pred_all_PBE[[low_iter]][test_idx]
    
    ## Prediction. MAE
    y_pred_mean = mu_y(phi_post)
    y_pred_var = y_pred_var_high(phi_post, low_variance = (pred_all_PBE_sd[[low_iter]][test_idx])^2)
    y_pred_sd = y_pred_sd_high(y_pred_var)
    y_true = as.numeric(dt_energy[test_idx, energy])
    
    df_pred_PBE0_pure[[current_iteration]] = data.frame("structure_id" = dt_structures[test_idx, structure_id],
                      "y_true" = as.numeric(dt_energy[test_idx, energy]),
                      "y_pred" = y_pred_mean,
                      "y_sd" = y_pred_sd,
                      "y_pred_min" = y_pred_mean - sd_coef*y_pred_sd,
                      "y_pred_max" = y_pred_mean + sd_coef*y_pred_sd,
                      "min_dist" = apply(D_all[test_idx, training_idx], 1, min))
      
    df_error_pure$seq_mae[current_iteration] = mean(abs(dt_energy[test_idx, energy] - y_pred_mean))
    df_error_pure$seq_rmse[current_iteration] = get_pred_rmse(y_true, y_pred_mean)
    
    ## Looking at ranks: true, predicted and ff
    df_pred_PBE0_pure[[current_iteration]]$true_rank = rank(df_pred_PBE0_pure[[current_iteration]]$y_true)
    df_pred_PBE0_pure[[current_iteration]]$pred_rank = rank(df_pred_PBE0_pure[[current_iteration]]$y_pred)
    df_pred_PBE0_pure[[current_iteration]]$ff_rank = rank(dt_energy$ff_energy[test_idx])
    
    PBE0_ff_true_rank_corr[current_iteration] = cor(df_pred_PBE0_pure[[current_iteration]]$ff_rank, df_pred_PBE0_pure[[current_iteration]]$true_rank,
                                                    method = "spearman")
    PBE0_pred_true_rank_corr[current_iteration] = cor(df_pred_PBE0_pure[[current_iteration]]$pred_rank, df_pred_PBE0_pure[[current_iteration]]$true_rank,
                                                    method = "spearman")
      
  }

}

```

Plotting everything

```{r}
for (low_iter in 1:n_training_iter_low) {
  training_percentage = training_proportion_low[n_training_iter_low - low_iter + 1] 
  
   ## Plotting predictions and true values for PBE, without error bars, with alpha and beta
  
  ggplot(data = df_pred_PBE[[low_iter]] , aes(x = y_true)) +
    geom_abline(colour = abline_colour) +
    geom_point(aes(y = y_pred), colour = pred_point_colour, pch = pred_point_type, size = pred_point_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == alpha_structure_id, "alpha", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == beta_structure_id, "beta", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    ggtitle(glue::glue("Predicted PBE. {training_percentage}% training set. MAE = {round(mae_low_track[low_iter], digits = 4)}")) +
    ylab(pred_ylab) + xlab(true_xlab) +
    theme_minimal() + theme(axis.title = element_text(size = axis_title_size),
                            axis.text = element_text(size = axis_tick_label_size),
                            legend.text = element_text(size = legend_title_size),
                            plot.title = element_text(size = title_size, colour = PBE_colour))
  ggsave(glue::glue("{getwd()}/results/plots/PBE_pred_true_{training_percentage}.jpeg"),
         width = plot_width, height = plot_height)

  # PBE With uncertainty bars  
  ggplot(data = df_pred_PBE[[low_iter]] , aes(x = y_true)) +
    geom_abline(colour = abline_colour) +
    geom_segment(aes(xend = y_true, y = y_pred_min, yend = y_pred_max), colour = pred_point_colour, size = interval_bar_width) +
    geom_point(aes(y = y_pred), colour = pred_point_colour, pch = pred_point_type, size = pred_point_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == alpha_structure_id, "alpha", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == beta_structure_id, "beta", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    ggtitle(glue::glue("Predicted PBE. {training_percentage}% training set."),
            subtitle = glue::glue(" MAE = {round(mae_low_track[low_iter], digits = 4)}")) +
    ylab(pred_ylab) + xlab(true_xlab) +
        theme_minimal() + theme(axis.title = element_text(size = axis_title_size),
                            axis.text = element_text(size = axis_tick_label_size),
                            legend.text = element_text(size = legend_title_size),
                            plot.title = element_text(size = title_size, colour = PBE_colour),
                            plot.subtitle = element_text(size = subtitle_size, colour = PBE_subcolour))
  ggsave(glue::glue("{getwd()}/results/plots/PBE_pred_true_bars_{training_percentage}.jpeg"),
         width = plot_width, height = plot_height)
  
  ff_cor = PBE_ff_true_rank_corr[low_iter] = cor(df_pred_PBE[[low_iter]]$ff_rank, df_pred_PBE[[low_iter]]$true_rank,
                                                    method = "spearman")
  pred_cor = PBE_pred_true_rank_corr[low_iter] = cor(df_pred_PBE[[low_iter]]$pred_rank, df_pred_PBE[[low_iter]]$true_rank,
                                                    method = "spearman") 
  
  cols = c( "col_ff" = ff_rank_colour, "col_pred" = pred_point_colour)
  shapes = c("s_ff" = 17, "s_pred" = 16)
  
  for (high_iter in 1:n_training_iter_high) {
    training_proportion = training_proportion_high[n_training_iter_high - high_iter + 1] 
    current_iteration = n_training_iter_high*(low_iter-1) + high_iter
    
    # Predictions for PBE0 with uncertainty bars -- pure test set
    
    ggplot(data = df_pred_PBE0_pure[[current_iteration]] , aes(x = y_true)) +
    geom_abline(colour = abline_colour) +
    geom_segment(aes(xend = y_true, y = y_pred_min, yend = y_pred_max), colour = pred_point_colour, size = interval_bar_width) +
    geom_point(aes(y = y_pred), colour = pred_point_colour, pch = pred_point_type, size = pred_point_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == alpha_structure_id, "alpha", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == beta_structure_id, "beta", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    ggtitle(glue::glue("Predicted PBE0. {training_percentage}%/{training_proportion}% training sets."),
            subtitle = glue::glue("MAE = {round(df_error_pure$seq_mae[current_iteration], digits = 4)}")) +
    ylab(pred_ylab) + xlab(true_xlab) +
        theme_minimal() + theme(axis.title = element_text(size = axis_title_size),
                            axis.text = element_text(size = axis_tick_label_size),
                            legend.text = element_text(size = legend_title_size),
                            plot.title = element_text(size = title_size, colour = PBE0_colour),
                            plot.subtitle = element_text(size = subtitle_size, colour = PBE0_subcolour))
    ggsave(glue::glue("{getwd()}/results/plots/PBE0_pred_true_bars_{training_percentage}_{training_proportion}.jpeg"), width = plot_width, height = plot_height)
    
  }
}
```

Running single-level GPs for PBE0 (with FF) on smaller training sets -- and testing on the pure test set.

```{r}
## Single GPs on smaller training sets only
mae_high_track = rmse_high_track = rep(0, n_training_iter_low)
df_single_PBE0_low = list("vector", n_training_iter_low)
df_single_PBE0_high = list("vector", n_training_iter_low*n_training_iter_high)

df_single_error = data.table(expand.grid(training_proportion_low[n_training_iter_low :1], training_proportion_high[n_training_iter_high :1]))
names(df_single_error) = c("high", "low")   # MAE and RMSE track on pure test set
df_single_error$mae = df_single_error$rmse = df_single_error$low_mae = df_single_error$low_rmse = 0.0

for (low_iter in 1:n_training_iter_low) {
  
  ## Specifying the response
  dt_energy$energy = dt_energy$high
  ## Reading training and test indices (pure test idx)
  training_percentage = training_proportion_low[n_training_iter_low - low_iter + 1] 
  training_idx = sort(read.table(glue::glue("{getwd()}/training_sets/tr_idx_low_{training_percentage}.txt"))$training_idx_low)
  test_idx = sort(read.table(glue::glue("{getwd()}/training_sets/pure_test_idx_{max(training_proportion_low)}.txt"))$pure_PBE0_test_idx)
  n_training = length(training_idx)
  n_test = length(test_idx)
  
  # Specifying linear part for PBE0 modelling - training and test
  linear_training = dt_energy[training_idx, ff_energy]
  linear_test = dt_energy[test_idx, ff_energy]
  
  # Optimising the posterior for phi_c
  phi_opt = phi_iso_optim()
  phi_post = phi_opt$phi_post   
  
  ## Prediction
  y_pred_mean = mu_y(phi_post)
  y_pred_sd = sqrt(diag(Sigma_y(phi_post))*as.numeric(gamma_(phi_post))/alpha_(n_training))
  y_true = as.numeric(dt_energy[test_idx, energy])
  
  ## Tracking MAE and RMSE
  mae_high_track[low_iter] = mean(abs(dt_energy[test_idx, energy] - y_pred_mean))
  rmse_high_track[low_iter] = get_pred_rmse(y_true, y_pred_mean)
  
  df_single_error$low_mae[df_single_error$low == as.character(training_percentage)] = mae_high_track[low_iter]     # errors when trained on a larger (low) set
  df_single_error$low_rmse[df_single_error$low == as.character(training_percentage)] = rmse_high_track[low_iter]
  
  ## Tracking predictions and errors
  df_single_PBE0_low[[low_iter]] = data.frame("structure_id" = dt_structures[test_idx, structure_id],
                                              "y_true" = as.numeric(dt_energy[test_idx, energy]),
                                              "y_pred" = y_pred_mean,
                                              "y_sd" = y_pred_sd,
                                              "y_pred_min" = y_pred_mean - sd_coef*y_pred_sd,
                                              "y_pred_max" = y_pred_mean + sd_coef*y_pred_sd,
                                              "min_dist" = apply(D_all[test_idx, training_idx], 1, min))
  
  ## Looking at ranks: true, predicted and ff
  df_single_PBE0_low[[low_iter]]$true_rank = rank(df_single_PBE0_low[[low_iter]]$y_true)
  df_single_PBE0_low[[low_iter]]$pred_rank = rank(df_single_PBE0_low[[low_iter]]$y_pred)
  df_single_PBE0_low[[low_iter]]$ff_rank = rank(dt_energy$ff_energy[test_idx])

  
  for (high_iter in 1:n_training_iter_high) {
    
    ## Specifying the response
    dt_energy$energy = dt_energy$high
    
    ## Reading training and test indices
    training_proportion = training_proportion_high[n_training_iter_high - high_iter + 1] 
    training_idx = sort(read.table(glue::glue("{getwd()}/training_sets/tr_idx_high_{training_proportion_low[n_training_iter_low-low_iter+1]}_
                              {training_proportion_high[n_training_iter_high-high_iter+1]}.txt"))$training_idx_high)
    n_training = length(training_idx)
    current_iteration = n_training_iter_high*(low_iter-1) + high_iter
   
    ###### Looking at PBE0 predictions at pure_test_set only
    test_idx = sort(read.table(glue::glue("{getwd()}/training_sets/pure_test_idx_{max(training_proportion_low)}.txt"))$pure_PBE0_test_idx)
    n_test = length(test_idx)
    linear_training = dt_energy[training_idx, ff_energy]
    linear_test = dt_energy[test_idx, ff_energy]
    
    # Optimising the posterior for phi_c
    phi_opt = phi_iso_optim()
    phi_post = phi_opt$phi_post   
    
    ## Prediction. MAE
    y_pred_mean = mu_y(phi_post)
    y_pred_sd = sqrt(diag(Sigma_y(phi_post))*as.numeric(gamma_(phi_post))/alpha_(n_training))
    y_true = as.numeric(dt_energy[test_idx, energy])
    
    df_single_PBE0_high[[current_iteration]] = data.frame("structure_id" = dt_structures[test_idx, structure_id],
                                                        "y_true" = as.numeric(dt_energy[test_idx, energy]),
                                                        "y_pred" = y_pred_mean,
                                                        "y_sd" = y_pred_sd,
                                                        "y_pred_min" = y_pred_mean - sd_coef*y_pred_sd,
                                                        "y_pred_max" = y_pred_mean + sd_coef*y_pred_sd,
                                                        "min_dist" = apply(D_all[test_idx, training_idx], 1, min))
    
    df_single_error$mae[current_iteration] = mean(abs(dt_energy[test_idx, energy] - y_pred_mean))
    df_single_error$rmse[current_iteration] = get_pred_rmse(y_true, y_pred_mean)
    
    ## Looking at ranks: true, predicted and ff
    df_single_PBE0_high[[current_iteration]]$true_rank = rank(df_single_PBE0_high[[current_iteration]]$y_true)
    df_single_PBE0_high[[current_iteration]]$pred_rank = rank(df_single_PBE0_high[[current_iteration]]$y_pred)
    df_single_PBE0_high[[current_iteration]]$ff_rank = rank(dt_energy$ff_energy[test_idx])
    
  }
}
```

Plotting predicted and true values for the single GPs for PBE0 (on larger training sets)

```{r}

for (low_iter in 1:n_training_iter_low) {

  training_percentage = training_proportion_low[n_training_iter_low - low_iter + 1] 
  
  ## Plotting predictions and true values, without error bars
  ggplot(data = df_single_PBE0_low[[low_iter]], aes(x = y_true)) +
    geom_abline(colour = abline_colour) +
    geom_point(aes(y = y_pred), colour = pred_point_colour, pch = pred_point_type, size = pred_point_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == alpha_structure_id, "alpha", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == beta_structure_id, "beta", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    ggtitle(glue::glue("Predicted PBE0. {training_percentage}% training set."),
            subtitle = glue::glue(" MAE = {round(mae_high_track[low_iter], digits = 4)}")) +
    ylab(pred_ylab) + xlab(true_xlab) +
        theme_minimal() + theme(axis.title = element_text(size = axis_title_size),
                            axis.text = element_text(size = axis_tick_label_size),
                            legend.text = element_text(size = legend_title_size),
                            plot.title = element_text(size = title_size, colour = PBE0_colour),
                            plot.subtitle = element_text(size = subtitle_size, colour = PBE0_subcolour))
  ggsave(glue::glue("{getwd()}/results/plots/PBE0_pred_true_{training_percentage}.jpeg"),
        width = plot_width, height = plot_height)
  
  # With uncertainty bars  
  ggplot(data = df_single_PBE0_low[[low_iter]] , aes(x = y_true)) +
    geom_abline(colour = abline_colour) +
    geom_segment(aes(xend = y_true, y = y_pred_min, yend = y_pred_max), colour = pred_point_colour, size = interval_bar_width) +
    geom_point(aes(y = y_pred), colour = pred_point_colour, pch = pred_point_type, size = pred_point_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == alpha_structure_id, "alpha", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == beta_structure_id, "beta", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    ggtitle(glue::glue("Predicted PBE0. {training_percentage}% training set."),
            subtitle = glue::glue(" MAE = {round(mae_high_track[low_iter], digits = 4)}")) +
    ylab(pred_ylab) + xlab(true_xlab) +
        theme_minimal() + theme(axis.title = element_text(size = axis_title_size),
                            axis.text = element_text(size = axis_tick_label_size),
                            legend.text = element_text(size = legend_title_size),
                            plot.title = element_text(size = title_size, colour = PBE0_colour),
                            plot.subtitle = element_text(size = subtitle_size, colour = PBE0_subcolour))
  ggsave(glue::glue("{getwd()}/results/plots/PBE0_pred_true_bars_{training_percentage}.jpeg"), width = plot_width, height = plot_height)
 
######################################################################

  
  for (high_iter in 1:n_training_iter_high) {
    
    training_proportion = training_proportion_high[n_training_iter_high - high_iter + 1] 
    current_iteration = n_training_iter_high*(low_iter-1) + high_iter
    
      # Predictions with uncertainty bars -- pure test set
    
    ggplot(data = df_single_PBE0_high[[current_iteration]], aes(x = y_true)) +
    geom_abline(colour = abline_colour) +
    geom_segment(aes(xend = y_true, y = y_pred_min, yend = y_pred_max), colour = pred_point_colour, size = interval_bar_width) +
    geom_point(aes(y = y_pred), colour = pred_point_colour, pch = pred_point_type, size = pred_point_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == alpha_structure_id, "alpha", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    geom_text(aes(y = y_pred, label = ifelse(structure_id == beta_structure_id, "beta", '')), hjust=1.5, vjust=1, parse = T, 
              colour = label_colour, size = label_text_size) +
    ggtitle(glue::glue("Predicted PBE0. {training_percentage}%*{training_proportion}% training sets."),
            subtitle = glue::glue(" MAE = {round(df_single_error$mae[current_iteration], digits = 4)}")) +
    ylab(pred_ylab) + xlab(true_xlab) +
        theme_minimal() + theme(axis.title = element_text(size = axis_title_size),
                            axis.text = element_text(size = axis_tick_label_size),
                            legend.text = element_text(size = legend_title_size),
                            plot.title = element_text(size = title_size, colour = PBE0_colour),
                            plot.subtitle = element_text(size = subtitle_size, colour = PBE0_subcolour))
    ggsave(glue::glue("{getwd()}/results/plots/PBE0_single_pred_true_bars_{training_percentage}_{training_proportion}.jpeg"), width = plot_width, height = plot_height)
    
      }
}

```

```{r}
## Calculate scores (CRPS)

PBE0_scores = read.csv(text = "fraction_PBE, fraction_PBE0, score")  # empty df

for (low_iter in 1:n_training_iter_low) {
  
  training_percentage = training_proportion_low[n_training_iter_low - low_iter + 1]
  n_training_low = floor(training_percentage*n_structures/100)
  
  for (high_iter in 1:n_training_iter_high) {
    
    training_proportion = training_proportion_high[n_training_iter_high - high_iter + 1] 
    current_iteration = n_training_iter_high*(low_iter-1) + high_iter  
    n_training = floor(training_proportion*n_training_low/100)

    df_current = df_pred_PBE0_pure[[current_iteration]]
    
    y_pred_var = (df_current$y_sd)^2
    scale_pars = (y_pred_var)*(alpha_(n_training) - 1)/alpha_(n_training)

    df_current$score = crps_t(y = df_current$y_true, df = 2*alpha_(n_training),
                   location = df_current$y_pred, scale = scale_pars)
    
    mean_score = mean(df_current$score)
    PBE0_scores[current_iteration, ] = c(training_percentage, training_proportion, mean_score)
  }

}

write.table(PBE0_scores, glue::glue("{getwd()}/results/OA_PBE0_scores.txt"), sep = "\t")
```


Saving the RData
```{r}
save.image(glue::glue("{getwd()}/results/OA_seqGP_output.RData"))
```


```{r}
## PCA of descriptors
n_col = ncol(dt_structures)

oa_pca = prcomp(dt_structures[, 5:n_col], center = TRUE)
summary(oa_pca$sdev)

oa.cov = cov(dt_structures[, 5:n_col])
oa.eigen.sum = sum(diag(oa.cov))

oa.eigen = eigen(oa.cov)
oa.eigen$vectors[,1]

for (s in oa.eigen$values) {
  print(s / oa.eigen.sum)
}

dt_eigen = data.table("Eigenvalue" = oa.eigen$values)
dt_eigen$molecule = "Oxalic Acid"
plot(oa.eigen$values[1:10], xlab = 'Eigenvalue Number', ylab = 'Eigenvalue Size', main = 'PCA of symmetry functions (OA)')
lines(oa.eigen$values[1:10])

write.table(oa.eigen$values[1:15], glue::glue("{getwd()}/OA_SF_eigenvalues.txt"))
```
